---
title: "Reproducible Research II"
author: "Adam M. Wilson"
date: "September 2015"
output:
  html_document:
      keep_md: true
---

```{r, echo=FALSE, message=FALSE, results='hide', purl=FALSE}
## This chunk automatically generates a text .R version of this script when running within knitr.  You do not need to run this...
input  = knitr::current_input()  # filename of input document
output = paste(tools::file_path_sans_ext(input), 'R', sep = '.')
knitr::purl(input,output,documentation=2,quiet=T)
knitr::opts_chunk$set(cache=T)
```

Load these packages in a code chunk:

```{r, message=F}
library(dplyr)
library(tidyr)
library(ggplot2)
library(maps)
library(spocc)
```


# Download data

## Daily ozone data from the EPA
The data are available from 1990 through 2015, but for now we'll just use 2013:2014.  If you want to extend the analysis, feel free to change this.  
```{r}
years=2013:2014

files=paste0("http://aqsdr1.epa.gov/aqsweb/aqstmp/airdata/daily_44201_",years,".zip")

files
```

### Create a directory to hold the data.
```{r}
datadir="data"
```

### Write a simple download function

1. Checks if file already exists
2. If needed, downloads the file.
3. Unzips the file into our `datadir`

```{r}
downloadData=function(file,overwrite=F){
  cfile=sub("zip","csv",file)%>%basename()  #get filename
  if(file.exists(file.path(datadir,cfile))) {
    return("File exists")
  }
  temp <- tempfile()  # make a filename for a temporary file
  download.file(file,temp)  # download the zipped file from the website
  unzip(temp,exdir=datadir)  # unzip the data to our datadir
  file.remove(temp)  # remove the zipped file
}
```
  

Try running that for just one year:
```{r}
downloadData(files[1])
```

### Download all desired years with a simple `for()` loop

```{r}
for(f in files){
  downloadData(f)
}
```


## Load Data

### Another function to load all available datasets
```{r}
loadData <- function(path) { 
  files <- dir(path, pattern = '\\.csv', full.names = TRUE)
  tables <- lapply(files, read.csv, stringsAsFactors=F)
  dplyr::bind_rows(tables)
}
```

> Use two colons (`::`) to call a function from a package without explicitly loading the package.

### Import the data

```{r}
d=loadData(datadir)

d
```


```{r}
d%>%
  separate(col=Date.Local,into=c("year","month","day"),sep="-")%>%
  group_by(Latitude,Longitude,year)%>%
  summarise(mean=mean(Arithmetic.Mean,na.rm=T))
```


## Get polygon layer of states
```{r}
usa=map("state")

d%>%filter(State.Name=="New York")%>%
  select(Latitude, Longitude, County.Name, Address)%>% distinct()

```

## Step 2: Load data


```{r} 
## define which species to query
sp='Turdus migratorius'

```
This can take a few seconds.

## Step 3: Map it

```{r, fig.width=6}
# Load coastline
map=map_data("world")

#ggplot(d,aes(x=longitude,y=latitude))+
##  geom_polygon(aes(x=long,y=lat,group=group,order=order),data=map)+
#  geom_point(col="red")+
#  coord_equal()
```


## Step 6:  Explore markdown functions

1. Use the Cheatsheet to add sections and some example narrative.  
2. Try changing changing the species name to your favorite species and re-run the report.  
3. Stage, Commit, Push!
4. Explore the markdown file on the GitHub website.  


## Colophon

Licensing: 
* Presentation: [CC-BY-3.0 ](http://creativecommons.org/licenses/by/3.0/us/)
* Source code: [MIT](http://opensource.org/licenses/MIT) 


## References

See Rmd file for full references and sources
