---
title: "Project-Related RMarkdown"
output:
  html_document:
    keep_md: yes
---

## Documentation

* [RMarkdown](http://rmarkdown.rstudio.com)
* [Knitr](http://yihui.name/knitr/)

## Document options

See `knitr::opts_chunk$get()` for all options and their defaults.

Set options for the full document with:
```{r}
knitr::opts_chunk$set(cache=F,
                      fig.width=7,
                      fig.height=4,
                      dpi=300,
                      dev="png")
```


## Code chunk settings
Chunk headers:

Show code and results with `echo=T` and `results='markup'` (the defaults):
```{r, echo=T, results='markup'}
2+2
```

Or hide code with:
```{r, echo=F}
2+2
```

Or hide results with:
```{r, results='hide'}
2+2
```

Or hide both with:
```{r, results='hide',echo=F}
2+2
```


### Messages
Some functions print output that you will want to hide in the report.  Use `message=F` to do this, especially for packages...

```{r}
library(rgdal)
```

Use `message=F` to hide message output.

```{r, message=F}
library(rgdal)
library(raster)
```

Other things to hide or show:

* warnings
* errors


## Caching for computationally intensive steps (e.g. >1 minute)

Caching stores temporary output so it does not need to be run every time the document is compiled.  See demos available [here](http://yihui.name/knitr/demo/cache/). 

### knitr caching
Set `knitr::opts_chunk$set(cache=T)` as above.  

* Knitr automatically keeps track of which chunks have been edited and what needs to be re-run.  
* Results saved in `cache` folder
* Usually works, but awkward for really large temporary files and sometimes tricky to get paths correct

### User-caching
An alternative is to write temporary files to disk and only calculate them when they don't already exist (or you want to overwrite them)

```{r}
library(raster)

datadir="/Users/adamw/GoogleDrive/Work/courses/2015_UB503/SpatialR"
ow=FALSE  # flag whether to overwrite existing files anyway

## Heavy step
fo=file.path(datadir,"data.tif")  # define output filename

if(!file.exists(fo) | ow){  # test if file exists or overwrite is desired

  r=raster(matrix(rnorm(1:100),nrow=10))   # do your computation
  # ...
  writeRaster(r,file=fo,overwrite=ow)  # write it out to disk

  }

```


## Options for writing captions in RMarkdown

### HTML

* Write a custom _hook_ as explained [here](https://github.com/yihui/knitr-examples/blob/master/063-html5-figure.Rmd).
* Use the [captioner package](https://github.com/adletaw/captioner/blob/master/vignettes/using_captioner.Rmd) (easier and more flexible!)


```{r}
library(captioner)
figure_nums = captioner(prefix = "Figure")
table_nums = captioner(prefix = "Table")
```

```{r}
plot(iris)
```
_`r figure_nums(name = "iris", caption = "Edgar Anderson's iris data.  All measurements are in centimetres.")`_

Then you can refer to a figure in the text with `r figure_nums("iris", display = "cite")`.

```{r, results='asis'}
library(xtable)
print(xtable(head(iris)),type = "html", include.rownames = F, align="center")
```
_`r table_nums(name = "iris", caption = "Edgar Anderson's iris data.  All measurements are in centimetres.")`_


See the data in `r table_nums("iris", display = "cite")`.

### PDF

Uses LaTeX to compile the document as explained [here](http://rmarkdown.rstudio.com/pdf_document_format.html).  

* Use `fig_caption: true` in the YAML header
* Use `fig.cap="your caption here"` in code chunk

Or use `captioner` as with HTML.



## Tables of regression models

```{r,message=F}
library(texreg)
```

```{r, messages=F, warning=F, results='asis'}
lm1=lm(rnorm(10)~rnorm(10))
## Xtable
print(xtable(lm1),type="html")

## HTMLreg
htmlreg(lm1,caption = "")
```
_`r table_nums(name = "r1", caption = "Regression of random variables")`_

## Rcpp

Compiling and calling functions written in C++ from R using the [`Rcpp` package](http://www.rcpp.org).  

## GGplot themes 

You can set the default themes for ggplot figures like this:
```{r}
library(ggplot2)
presentation_theme <- theme_grey()+
  theme(text = element_text(size = 25, colour = "black"))
theme_set(presentation_theme)
```
Then all ggplot plots will use those defaults.

# Data

## Historical climate data

Check out the `prism` package for gridded time series of historical US weather: https://github.com/ropensci/prism
